### 2015-02-19 fundamentals/impl.tex
cleanup

A modular, agent-based approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice to
build \Cyclus on open source libraries in modern programming languages enables
both remote and multiprocess execution on a number of platforms. This section begins by
describing the general design features that make \Cyclus both flexible and powerful:
cluster-ready software and dynamic libraries.  Next, the framework using an
\gls{ABM} paradigm, which provides an expansion in performance beyond typical systems dynamics
capabilities, is described, focusing on agent interchangeability and the
implementation of the region-institution-facility hierarchy.
Next, the discrete treatment of objects is discussed in terms of both
resources and materials and time via the \gls{DRE}.
Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.
Lastly, the methods for quality assurance are outlined.

>>>>

A modular, \acrfull{ABM} approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice to
build \Cyclus on open source libraries in modern programming languages enables
both remote and multiprocess execution on a number of platforms. This section begins by
describing the general design features that make \Cyclus both flexible and powerful:
cluster-ready software and dynamic libraries.  Next, the framework has an
\gls{ABM} paradigm, which provides an expansion in performance beyond typical system dynamics
capabilities, is described, focusing on agent interchangeability and the
implementation of the region-institution-facility hierarchy.
Next, the discrete treatment of objects is discussed in terms of both
resources and materials and time via the \gls{DRE}.
Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.
Lastly, the methods for quality assurance are outlined.
